---
title: "CX-SPE Method Paper Control Script"
author: "Joshua Sacks"
date: '2022-07-12'
output: html_document
---



Section 1: Analytical Validation

Part 1: Read in, parse, and normalize skyline output 

```{r, echo=FLASE, message=FALSE, error = FALSE, warning=FALSE}
##Parse Skyline data for CX-SPE Samples
source("R_Code/AV_CX_HILIC_Parse.R")
remove(list = ls())
source("R_Code/AV_CX_RP_Parse.R")
remove(list = ls())

##Run BMIS Normalization on Skyline CX-SPE Data
source("R_Code/AV_CX_HILIC_BMIS.R")
remove(list = ls())
source("R_Code/AV_CX_RP_BMIS.R")
remove(list = ls())

###Parse Skyline Data for PPL-SPE
source("R_Code/AV_PPL_HILIC_Parse.R")
remove(list = ls())
source("R_Code/AV_PPL_RP_Parse.R")
remove(list = ls())

##Run BMIS Normalization on Skyline PPL-SPE Data
source("R_Code/AV_PPL_HILIC_BMIS.R")
remove(list = ls())
source("R_Code/AV_PPL_RP_BMIS.R")
remove(list = ls())

##Combine HILIC and RP data
source("R_Code/AV_HILIC_RP_Combine.R")
remove(list = ls())
```


Part 2: Run code to evaluate CX-SPE and PPL-methods for targeted compounds

```{r, echo=FALSE, message=FALSE, error = FALSE, warning=FALSE}
#R2 calculations
source("R_Code/AV_CX_R2_Calcs.R")
remove(list = ls())

#Extraction effiency and response factor calculations for CX-SPE and PPL-SPE
source("R_Code/AV_EE_RF_Calcs.R")
remove(list = ls())

#Identify "High Quality" Compounds based on user defined thresholds for EE, RSD, and R2
source("R_Code/AV_Quality_Control.R")
remove(list = ls())

#Compare CX-SPE and PPL-SPE in targeted space
source("R_Code/AV_CX_PPL_Comparison.R")
remove(list = ls())

#Run ANOVAs to determine if sample matrix has a significant effect on method performance:
source("R_Code/AV_CX_ANOVAs.R")
remove(list = ls())


```



Section 2: Targeted Environmental Samples

Part 1: Read in, parse, and normalize skyline output

```{r echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
##Parse Skyline data for CX-SPE + PPL-SPE Samples
source("R_Code/ES_CX_HILIC_Parse.R")
remove(list = ls())
source("R_Code/ES_CX_RP_Parse.R")
remove(list = ls())

##Run BMIS Normalization on Skyline CX-SPE Data
source("R_Code/ES_CX_HILIC_BMIS.R")
remove(list = ls())
source("R_Code/ES_CX_RP_BMIS.R")
remove(list = ls())


##Run BMIS Normalization on Skyline PPL-SPE Data
source("R_Code/ES_PPL_HILIC_BMIS.R")
remove(list = ls())
source("R_Code/ES_PPL_RP_BMIS.R")
remove(list = ls())
```

Part 2: Run QC Code, Determine RFs and RF ratios, quantify environmental concentrations and limits of detection, and summarize results

```{r, echo=hide, message=FALSE, error = FALSE, warning=FALSE, results = "hide"}
##Run Blk-QC Code for CX-SPE
source("R_Code/EX_CX_HILIC_Blk_QC.R")
remove(list = ls())
source("R_Code/ES_CX_RP_Blk_QC.R")
remove(list = ls())

##Run Blk-QC Code for PPL-SPE
source("R_Code/ES_PPL_HILIC_Blk_QC.R")
remove(list = ls())
source("R_Code/ES_PPL_RP_Blk_QC.R")
remove(list = ls())

##Determine RF and RFratios
source("R_Code/ES_HILIC_RF_RFratio_calcs.R")
remove(list = ls())
source("R_Code/ES_RP_RF_RFratio_calcs.R")
remove(list = ls())

##Run CX-SPE Quantification Code
source("R_Code/ES_CX_HILIC_Quantification.R")
remove(list = ls())
source("R_Code/ES_CX_RP_Quantification.R")
remove(list = ls())

##Run PPL-SPE Quantification Code
source("R_Code/ES_PPL_HILIC_Quantification.R")
remove(list = ls())
source("R_Code/ES_PPL_RP_Quantification.R")
remove(list = ls())

###Summzarize CX-SPE and PPL-SPE Results
source("R_Code/ES_CX_LOD_Conc_Summary.R")
remove(list = ls())
source("R_Code/ES_PPL_Conc_Summary.R")
remove(list = ls())
```

Section 3: Untargeted Analysis
```{r, echo=FALSE, message=FALSE, error = FALSE, warning=FALSE}
##Parse and Normalize MS-DIAL Output
source("R_Code/Untargeted_HILIC_BMIS.R")
remove(list = ls())
source("R_Code/Untargeted_RP_BMIS.R")
remove(list = ls())

##Apply Quality Control Thresholds to Untargeted data output
source("R_Code/Untargeted_QC_Tidy.R")
remove(list = ls())

##Run Statistical Comparisons of untargeted CX-SPE and PPL-SPE data
source("R_Code/Untargeted_Analysis.R")
remove(list = ls())

##Run Statistical Comparisons of untargeted CX-SPE and PPL-SPE data
source("R_Code/Untargeted_Targeted_Comparison.R")
remove(list = ls())

```





Section 4: Figures
```{r, echo=FALSE, message=FALSE, error = FALSE, warning=FALSE}
##Main Text figure 2
source("Figures/R_Code/AV_EE_RF_Plots.R")
remove(list = ls())

##Main Text figure 3 and supplmental figure 2
source("Figures/R_Code/AV_EE_RF_Plots.R")
remove(list = ls())

##Run Statistical Comparisons of untargeted CX-SPE and PPL-SPE data
source("R_Code/Untargeted_Analysis.R")
remove(list = ls())

##Run Statistical Comparisons of untargeted CX-SPE and PPL-SPE data
source("R_Code/Untargeted_Targeted_Comparison.R")
remove(list = ls())
```




Section 5: Tables
```{r, echo=hide, message=FALSE, error = FALSE, warning=FALSE, results = "hide"}
##Run Blk-QC Code for CX-SPE
source("R_Code/EX_CX_HILIC_Blk_QC.R")
remove(list = ls())
source("R_Code/ES_CX_RP_Blk_QC.R")
remove(list = ls())


```


























## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
